\chapter{Design Patterns}
    JobAdder's design is object-oriented. As such, it uses a lot of the common design patterns.
    \section{Strategy}
        The Strategy design pattern is used for abstracting away the scheduling algorithm specifics.
        It allows a complete replacement of the algorithm, as well as easier testing of the other components.

        The default scheduling algorithm itself uses several (Sub)Strategies: The ordering of jobs by their effective
        priority(CostFunction) and the assignment of Work machines for jobs (JobDistributionPolicy).

        Another Strategy is the DockerContext class. It allows the User client to control how the Dockerfile of the Job
        is built.
    \section{Template method}
        The default JobDistributionPolicies all work in the same way - iterating over the available work machines,
        calculating assignment cost, and then picking the machine with the lowest cost. Using a
        base class DefaultJobDistributionPolicy which implements this logic, and leaving derived classes to implement
        the template method \_assign\_machine\_cost allows better code reuse and structuring.

    \section{Facade}
        The Facade design pattern is evident in the ServerDatabase, where it allows a convenient usage of the underlying
        database and acts as a gateway to the whole Server for all Commands sent from users and work machines.

    \section{Proxy}
        The Proxy design pattern in the Proxy subclasses allows easy access to remote components of JobAdder, without involving
        network communication in most of the codebase.

    \section{Abstract Factory}
        The IWorkerProxyFactory is an Abstract Factory. This allows reuse of WorkerProxy objects, as well as decouples the Dispatcher
        class from the Database class.

    \section{Memento}
        All classes that are Serializable can be thought of as a variation of the Memento design pattern.
        These classes can convert their internal state to a dictionary and then be recreated from that.

    \section{Observer}
        The observer design patter is indirectly present in the design. The ServerDatabase provides two callbacks
        for classes that need to process updates in the database(Scheduler and EmailNotifier). The SSHConnection class
            provides the option to register a callback for the case when the connection is unexpectedly closed(used for
            deregistering work machines). In both cases, it enables loose coupling between classes of different packages.
