\section{Work machine client(WMC)}
  \subsection{Functional requirements}
    \subsubsection{Main features}
    \begin{enumerate}
      \item[WMCF10] On startup, WMC shall connect to the server and report its hardware capabilities.
      \item[WMCF20] WMC must be able to receive commands from the central server.
      \item[WMCF30] Each work machine must have a single instance of WMC running.
      \item[WMCF40] WMC shall support the following commands:
      \begin{enumerate}
        \item[WMCF41] Start/Resume execution of a job.
        \item[WMCF42] Pause execution of a job.
        \item[WMCF43] Remove a job from the list of running jobs on the current machine.
        \item[WMCF44] Query the current state of the work machine: running jobs, load on hardware.
        \item[WMCF45] Terminate this instance of the WMC.
      \end{enumerate}
      \item[WMCF50] WMC shall download the job data to the local storage if needed. (TODO: need to decide when)
      \item[WMCF60] WMC shall notify the server whenever a job is completed.
    \end{enumerate}

    \subsubsection{Optional features}
      \begin{enumerate}
        \item[WMCFO10] WMC shall notify the server periodically on the progress of the job.
        \item[WMCFO20] WMC shall decide what kind of local storage to use for each job. (RAM, SSD or HDD).
        \item[WMCFO30] WMC shall estimate the time of arrival of a job.
      \end{enumerate}

  \subsection{Product Data}
  \begin{enumerate}
    \item[WMCPD10] Docker containers for all the jobs running on this machine.
    \item[WMCPD20] Results of the jobs running on this machine.
  \end{enumerate}
