\subsection{Functional requirements}
\subsubsection{Main features}
\begin{enumerate}
  \item[CSF10] The central server shall distribute \glspl{job}
    among the available work machines using the scheduling algorithm.
  \item[CSF20] Central server shall accept the following requests:
  \begin{enumerate}
    \item[CSF21] Schedule a new \gls{job} for execution.
    \item[CSF22] Terminate a \gls{job}.
    \item[CSF23] Initiate a SSH tunnel to a \gls{job}'s container, provided that the
      \gls{job status} is Running, Done or Killed, but the corresponding docker image
      has not been deleted yet.
  \end{enumerate}
    Each command should also contain information(\gls{UID}, \gls{GID}) about the actual user submitting the job.
  \item[CSF30] Only processes whose effective user is root shall be allowed to create the requests in CSF20.
  \item[CSF40] The central server shall include a utility program to create the requests described in CSF20.
    Each such utility program shall submit the request with the appropriate real \gls{UID} and real \gls{GID}
    of the user running the utility program.

  \item[CSF50] Central server shall provide network API to:
  \begin{enumerate}
    \item[CSF51] Get statistics about workload of the connected worker machines.
      For each work machine:
      \begin{itemize}
        \item CPU Load in percentage.
        \item Amount of free and used CPU threads.
        \item Amount of free and used RAM.
        \item Amount of free and used swap space.
        \item Work machine \gls{ID}.
      \end{itemize}
    \item[CSF52] Get information about a job given its \gls{ID}:
    \begin{itemize}
      \item The user which the job belongs to.
      \item \Gls{job priority}
      \item \Gls{job status}
      \item \Gls{timestamp} of when the job was scheduled.
      \item \Gls{timestamp} of when the job has finished running.
      \item Total amount of time spent in queue.
      \item If \gls{job status} is not Queued:
      \begin{itemize}
        \item Total amount of time spent running.
        \item Number of allocated CPU cores.
        \item Allocated RAM for the job in megabytes.
        \item Current utilization of allocated CPU cores, in percentage.
        \item Current utilization of allocated RAM, in percentage.
      \end{itemize}
    \end{itemize}
    \item[CSF53] Get a list of \glspl{ID} of jobs belonging to a given user.
    \item[CSF54] Get a list of \glspl{ID} of jobs which have been running in the
      past X hours.
    \item[CSF55] Get a list of \glspl{ID} of jobs which are running on the work machine with the given
      \gls{ID}.
  \end{enumerate}
  \item[CSF60] The requests described in CSF40 shall be accessible by any user or external entity.
\end{enumerate}
