\section{Requirements}

\subsection{Mandatory}
\begin{itemize}
\item JA must assign user jobs to work machines.
 \item JA must provide a user client on which a user can make job requests.
\item JA must be accessible through a CLI.
\item Users can specify a priority for a job.
\item Users can specify the minimum hardware requirements for a job: RAM, CPU thread count, GPU memory/model/speed.
\item Users can specify an operating system on which the job should be run.
\item The system must store all the data of queued, running and fulfilled jobs.
\item The stored data should not get lost on a system crash or restart.
\item Users can query the state of running jobs from a web interface or an API.
\item Users can start, pause, resume and interrupt a running job.
\item Users must be notified once a job is completed.
%not really sure about how to include the following item in the requirements.
\item JA has the same functionality as a normal work machine.
\end{itemize}

\subsection{Optional}
\begin{itemize}
\item Blocking mode: wait for the job to finish before client returns.
\item Path translation: handle different mount point locations.
\item Attach to stdout of running job or read log output (something like ”tail
-f”).
\item Estimate ETA for running jobs.
%There will be more.
\end{itemize}

\subsection{Limits}
\begin{itemize}
\item Users cannot edit the specifications of a job once it's requested.
\item Users cannot interrupt, pause or resume jobs they didn't start.
\end{itemize}
